### 2019-03-26 1_introduction.tex
Tweak introduction line breaking.

We conduct a comprehensive comparative study of Task Bench
implementations in 13 different programming systems, including
Chapel~\cite{Chapel07}, Charm++~\cite{Charmpp93}, MPI~\cite{MPI},
OmpSs~\cite{OmpSs11}, OpenMP~\cite{OpenMPSpec40},
PaRSEC~\cite{PARSEC13}, Realm~\cite{Realm14}, Regent~\cite{Regent15},
Spark~\cite{Spark10}, StarPU~\cite{StarPU11},
Swift/T~\cite{Wozniak13}, TensorFlow~\cite{TensorFlow15}, and
X10~\cite{X1005}. Using METG(50\%), we determine the baseline
runtime overhead of each system along with overheads associated with
increasing numbers of and/or variations in the pattern of dependencies. We
also explore each system's ability to scale, hide communication
overhead, and mitigate load imbalance.

>>>>

We conduct a comprehensive comparative study of Task Bench
implementations in 13 different programming systems, including
Chapel \cite{Chapel07}, Charm++ \cite{Charmpp93}, MPI \cite{MPI},
OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
Spark \cite{Spark10}, StarPU \cite{StarPU11},
Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
X10 \cite{X1005}. Using METG(50\%), we determine the baseline
runtime overhead of each system along with overheads associated with
increasing numbers of and/or variations in the pattern of dependencies. We
also explore each system's ability to scale, hide communication
overhead, and mitigate load imbalance.
